---
title: "Introduction"
author: "Steve Pederson"
date: "23 November 2016"
output: 
  ioslides_presentation:
    css: custom.css
    fig_caption: yes
    keep_md: yes
    logo: images/UoA_logo_col_vert.png
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      warning = FALSE, message = FALSE, 
                      out.width = 800, fig.align = "center")
```

```{r, loadPackages}
library(knitr)
```

## Who Am I? | Steve Pederson

- R User for >10 years
- Co-ordinator, Bioinformatics Hub  
    - Level 4, Santos Petroleum Engineering Building

Also helping today:

- Alastair Ludington (Bioinformatics Hub)

## What is R

- Began as a statistical tool in the 1990s (Ross Ihaka & Robert Gentleman)
- Evolved far beyond it's original design
- Primarly used for analysis & graphics
- Also growing strong "Big Data" capabilities

## What is R

- Can be treated as a calculator:

```{r, echo=TRUE, include=TRUE, results='markup'}
1 + 2
```


## What is R

- Contains all mathematical functions `+`, `-`, `*`, `/`
- Exponents are defined using `^`

```{r echo=TRUE, include=TRUE, results='markup'}
2^3
1 + 2 - 3 * 4 / 5
```

